My title

### 2022-02-28 outputs/paper/paper.Rmd

>>>>

## Data Source
We generated data from U.S. Birth Rate 1950-2022[@birthrate]. We selected top 3 countries that are affected most and least by the Great Recession according to rankings determined by comparing currency devaluations, equity market declines, and rising sovereign bond spreads These measures tend to track developments in the real economy during times of economic crisis when financial strain handicaps consumption, investment, and in many cases government spending, which limits GDP and employment growth[@rank].
